ADNI EDA

### 2023-12-05 eda/adni_eda.Rmd
reorg

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data, data.table, nlme, devtools, slider)

@@

```{r}
adni.df.no_dup <- adni.df.filt %>%
  arrange(age_days) %>%
  group_by(participant) %>%
  slice(1)

@@

```{r}
ggplot(adni.df.no_dup) +
  geom_histogram(aes(x=age, fill=site), position="identity", alpha=0.5)
```

@@

```{r}
ggplot(adni.df.no_dup, aes(x=site, y=age, fill=dx, color=dx)) + 
  geom_boxplot() 
```

@@

>>>>

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data, data.table, nlme, devtools, slider, see)

@@

```{r}
adni.df.no_dup <- adni.df.filt %>%
  arrange(age_days) %>%
  group_by(participant) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(site) %>%
  filter(n() >= 2) %>%
  ungroup() #drop sites w <2 ppl

@@

```{r}
ggplot(adni.df.no_dup) +
  geom_violin(aes(x=site, y=age), scale="width", trim = FALSE, adjust=0.75)
```

@@

```{r}
ggplot(adni.df.no_dup, aes(x=site, y=age, fill=dx, color=dx)) +
  geom_violin(scale="width", trim = FALSE, adjust=0.75)
```

@@

Keep just CN, AD, and LMCI (same as longComBat paper)

```{r}
adni.df.no_dup %>%
  dplyr::filter(dx == "CN" | dx == "AD" | dx == "LMCI") %>%
ggplot() +
  geom_bar(aes(y=..count../tapply(..count.., ..x.. ,sum)[..x..], x=site, fill=dx)) + 
  scale_y_continuous(labels = scales::percent)

adni.df.no_dup %>%
  dplyr::filter(dx == "CN" | dx == "AD" | dx == "LMCI") %>%
ggplot() +
  geom_bar(aes(x=site, fill=dx))
```
